---
title: "Data Cleaning"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Steps in Data Cleaning

## Step 1: visually inspect
Let's install our packages first:
```{r}
pacman::p_load(
  rio,        # importing data  
  here,       # relative file pathways  
  janitor,    # data cleaning and tables
  lubridate,  # working with dates
  epikit,     # age_categories() function
  tidyverse   # data management and visualization
)
```

We will be using the original data from Fulton County in Excel format

The `rio` package can be used to import the file:
(the R project has been set up first with data sub-folder)
```{r}
list_raw <- import(here("data", "covid_example_data", "covid_example_data.xlsx"))
```

There are some quick checks to see if data imported including:  
- checking the console to ensure no error messages  
- checking Environment window: should see `list_raw` in Data with number of obs and variables

However, we will want to take a closer look:
`str` from base R allows us to see the structure of the data set incl. variable (column) names, types and values for the first few observations (rows):
```{r}
str(list_raw)
```

We can also see the same information in a cleaner form using the `tidyverse`
```{r}
glimpse(list_raw)
```


## Step 2: rename and select


## Step 3: clean dates, categorical, numerical


## Step 4: filter and remove duplicates
